Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-10-24 paper/main.tex
updated editorial policy checklist and reporting summary, also split out data and code availability sections as requested by editor

\section*{Data and code availability}

All of the data analyzed in this manuscript, along with all of the code for
running our experiment and carrying out the analyses may be found at
https://github.com/Con\-text\-Lab/eff\-ic\-ient-learn\-ing-khan.

>>>>

\section*{Data availability}

All of the data analyzed in this manuscript may be found at
https://github.com/Con\-text\-Lab/eff\-ic\-ient-learn\-ing-khan.

\section*{Code availability}

All of the code for running our experiment and carrying out the analyses may be
found at https://github.com/Con\-text\-Lab/eff\-ic\-ient-learn\-ing-khan.
